\chapter{Abstract}
The aim of this project was to develop a search system that uses the patient record notes for the current patient as a search query to the various chapters of the medicine handbook. This problem, would preferably be solved by employing one or several information retrieval methods. We have been working in the context of the Vector Space Model.

\begin{description}
\item{\textbf{Objectives:}} \\
The main objective of the project ,was to try out methods in information retrieval, while building a system that responds to queries, with a list of ranked, relevant documents.
\item{\textbf{How it was done:}} \\
We followed the completion of the tasks given in the assignment, step by step. A successful implementation of the tasks , would mark the right solution. The gold standard, can be used to measure our achievement. 
\item{\textbf{Results obtained:}}
The results obtained by using our system, can be extracted by comparing the list of our retrived documents, with those of the Gold Standard.  6/8 case searches had a gold standard chapter as the top hit. There were also some exceptions, like case 5, which has no relevant chapters. While case 7, gave us gold chapters on 2. and 4. place. The last thing to be mentioned, is that gold standard chapters can be found via the top  4 hits of our respective case search results.
\item{\textbf{Significance of results:}}
Arguing about the results, we can say that the implementation of VSM, turned out to work well for this information retrieval case. We were not constrained to use LSI, even though it’s a more sophisticated method, because VSM was working equally well. 
\end{description}