\chapter{Limitations given by the assignment}

One of the limitations given in this project, was that we had to choose between approved libraries on the course homepage. 
The information given in the assignment, was in the start confusing and some parts did not match what we actually got of resources on the homepage/it’s learning. Since we did not get any good introduction to the project we asked a lot in the start, but did not get any good answers. This was confusing because we were given a time limit of one month. \\

The assignment presents several requierments or limitations if you will to  our solution.
\begin{enumerate}
\item{Autocoding ICD-10}
\begin{enumerate}
\item{Find relevant ICD-10 codes based on match between the description part of the ICD-10 codes and the sentences in the clinical notes for each sentence in the clinical notes.}
\item{To store relation between sentence and code, make a table where each row contains the document number, sentence number followed by the relevant ICD-10 codes (ranked).}
\item{Do the same for the therapy chapters in Legemiddelhåndboka. Only include subchapters and subsubchapters.}
\end{enumerate}
\item{Autocoding ATC}
\begin{enumerate}
\item{Do same as with Autocoding ICD-10, but with ATC classification instead.}
\end{enumerate}
\item{Ranking using vector models}
\begin{enumerate}
\item{We are to use an information retrieval method for extracting and comparing semantic information in documents, based on statistical information.}
\end{enumerate}
\item{Evaluation}
\begin{enumerate}
\item{We shall write a report where we propose techniques/methods for evaluating the results automatically.}
\item{For each unique method write an evaluation.}
\end{enumerate}
\item{Improving the ranking}
\begin{enumerate}
\item{We shall only use the codes from task 1 and 2 to select and rank relevant chapters in Legemiddelhåndboken.}
\item{We shall combine the rresults from 6.a with the results from task 3. We will have to find a way to weight the different rankings given by the two approaches.}
\end{enumerate}
\item{Gold standard}
\begin{enumerate}
\item{We shall evaluate our different ranking methods with the gold standard provided by the course coordinator.}
\end{enumerate}
\item{Possible improvements}
\begin{enumerate}
\item{We shall propose ways to extend and improve the methods.}
\end{enumerate}
\end{enumerate}